An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-09-01 EconGrowth.Rnw
Deleted several blank lines.
Added a section about sigma^{\prime} transform.
Testing GitHub.

@@

Coefficients for each resampled CES model (without energy)
are shown in 
Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph}--\ref{fig:CES_sigma_delta_Cloud_Graph}.

@@

Coefficients for each resampled CES model (with $x$, ($kl$)$e$ nesting)
are shown in 
Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESx_sigma_delta_Cloud_Graph}.

>>>>

% small change to test GitHub.

@@

Coefficients for each resampled CES model (without energy)
are shown in 
Figures~\ref{fig:CES_lambda_gamma_Cloud_Graph}--\ref{fig:CES_sigma_delta_Cloud_Graph}. 
Note that transformed $\sigma$ and $\sigma_1$ values 
($\sigma^{\prime}$ and $\sigma_1^{\prime}$) are plotted to compress 
$2 < \sigma < \infty$ into $2 < \sigma^{\prime} \le 2.5$
($2 < \sigma_1 < \infty$ into $2 < \sigma_1^{\prime} \le 2.5$):

\begin{equation} \label{eq:sigma_transform}
  \sigma^{\prime} = 
    \begin{cases}
      \sigma,   & 0 \le \sigma \le 2\\
      1.5-\rho, & \sigma > 2
    \end{cases}
\end{equation}

\begin{equation} \label{eq:sigma_1_transform}
  \sigma_1^{\prime} = 
    \begin{cases}
      \sigma_1,   & 0 \le \sigma_1 \le 2\\
      1.5-\rho_1, & \sigma_1 > 2
    \end{cases}
\end{equation}

@@

Coefficients for each resampled CES model (with $x$, ($kl$)$e$ nesting)
are shown in 
Figures~\ref{fig:CESx_lambda_gamma_Cloud_Graph_kle}--\ref{fig:CESx_sigma_delta_Cloud_Graph_kle}.
